%
% $RCSfile: problem_analysis.tex,v $
%
% Copyright (c) 2001-2004. Christian Heller. All rights reserved.
%
% No copying, altering, distribution or any other actions concerning this
% document, except after explicit permission by the author!
% At some later point in time, this document is planned to be put under
% the GNU FDL license. For now, _everything_ is _restricted_ by the author.
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% @author Christian Heller <christian.heller@tuxtax.de>
%

\subsection{Problem Analysis}
\label{problem_analysis_heading}

Quality of software is often defined by its maintainability, extensibility and
flexibility. In the past decades, \emph{Procedural (Structured) Programming},
then \emph{Object Oriented Programming} (OOP) and more recently \emph{Component
Oriented Programming} (COP) provided a number of helpful paradigms to help to
achieve these goals. A major improvement was the extension of data \emph{Type}
to \emph{Class}, owning inheritable properties and methods.\\
But still, design problems are evident, in nearly every software product.
It is the \emph{false combination and grouping} of classes that still keeps us
away from clear and effective solutions. As a system grows, the interdependencies
between its single parts grow with. Why does this happen? Simply because a clear
architecture is missing. Even if developers really try to follow a such --
on some point in the software's life, compromises have to be made due to
unforeseen requirements and dependencies:
\begin{itemize}
    \item[-] \emph{Interfaces} are used to realize new properties by
        \emph{multiple inheritance} (\emph{Mix-In})
    \item[-] \emph{Static manager objects} accessible by any other objects in a
        system are introduced
    \item[-] New software layers are plugged in with \emph{varying mechanisms}
    \item[-] \emph{Redundant code} needs to be written (per copy \& paste),
        to avoid too many unwanted interdependencies
\end{itemize}

Can this be avoided at all and if, then how? The author's opinion is \emph{yes}
and the new concept introduced in this document can hopefully contribute a small
part to this, and show ways out of the misery.

