%
% $RCSfile$
%
% Copyright (c) 2002-2006. Christian Heller. All rights reserved.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision$ $Date$ $Author$
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\subsubsection{Container Unification}
\label{container_unification_heading}

Section \ref{motivation_heading} mentioned container inheritance as one problem
of current software. Due to polymorphism, it may cause unpredictable behaviour
possibly leading to \emph{falsified} container contents \cite{javaiaq}. The
previous sections introduced a knowledge schema which they claimed to be
\emph{general}. But that also means that all kinds of containers must be
representable by the suggested schema. But why are there so many different
kinds of containers? What actually is a container?

It is a concept expressing that some model \emph{contains} some other model(s).
Types of containers are, for example: \emph{Collections} (Array, Vector, Stack,
Set, List), \emph{Maps} (Hash Map, Hash Table) and the \emph{Tree}. They all
are containers. What differs, is just the meta information they store about
their elements. A list, for example, holds position information about each of
its elements. A map relates the name of an element to its model (1:1). A tree
links one model to many others (1:n).

But does the different meta information a container holds about its elements
justify the existence of different container models? If a knowledge schema was
general enough to represent a container structure on one hand, and to express
different kinds of meta information on the other, it might be able to behave
like any of the known container types.

The schema proposed in this work claims to be this kind of knowledge schema. It
has a container structure by default, and can thus hold many parts in a
\emph{Tree}-like manner. It holds standard meta information about its parts:
their \emph{Name}, \emph{Model}, kind of \emph{Abstraction} and further meta
information called \emph{Details} -- and is therefore able to link the name of
an element to its model, in a \emph{Map}-like manner. To the additional meta
information (details) may belong the \emph{Position} of an element within its
model, in a \emph{List}-like manner. A \emph{Table} structure can be represented
as well, by splitting it into a hierarchical (tree-like) representation, as
known from markup languages like the \emph{Hypertext Markup Language} (HTML).

Section \ref{cybol_heading} will introduce a language capable of expressing all
aspects of the knowledge schema as proposed here.
