%
% $RCSfile: property_bundling.tex,v $
%
% Copyright (c) 2001-2004. Christian Heller. All rights reserved.
%
% No copying, altering, distribution or any other actions concerning this
% document, except after explicit permission by the author!
% At some later point in time, this document is planned to be put under
% the GNU FDL license. For now, _everything_ is _restricted_ by the author.
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% @author Christian Heller <christian.heller@tuxtax.de>
%

\subsection{Property Bundling}
\label{property_bundling_heading}

Software consists of data which can be processed by a computer. This is possible
because \emph{qualitative} data are transformed into \emph{quantitative} data and,
finally, to \emph{Zero} and \emph{One}. \emph{Mathematics} delivers the \emph{Logic}
(\emph{Operations}) after which \emph{States} (\emph{Operands}) can be mapped,
to deliver the expected results.

When combining a number of operations in a certain order, an \emph{Algorithm} is
retrieved. The operands it works with are stored in \emph{Variables}. As can be
seen, there is always \emph{static} and \emph{dynamic} structures involved, the
static holding the states and the dynamic holding the rules for mapping between
states.

\emph{Structured}/ \emph{Procedural Programming} languages were the first to
explicitly provide the means to model static \emph{Structures} as well as dynamic
\emph{Procedures} (or \emph{Functions}, respectively). Both can be cascaded in
\emph{Hierarchies} and even use \emph{Recursion} for that.

Yet other synonyms for static and dynamic structures that were introduced by the
nowadays more popular \emph{Object Oriented Programming} (OOP) are \emph{Attribute}
and \emph{Method}. Both can be properties of an \emph{Object} which is the runtime
instance of a \emph{Class} which in turn represents the data \emph{Type}. A class
can \emph{inherit} properties from a \emph{super} class. This \emph{Inheritance}
was a truely new and innovative concept brought in by OOP. The \emph{Bundling} of
static and dynamic properties (attributes and methods), on the other hand, causes
more system interdependencies and complications than were predictable. It is a big
disadvantage that affects all modern object-oriented systems.

Certainly, the bundling stems from best intentions to receive cleaner code by
keeping not only attributes but also methods in a common module, such avoiding
\emph{wild} and \emph{global} procedures. But now, modules not only had to refer
to other modules for accessing their data; the same was needed for accessing methods.
With OOP, the number of cross-relations between modules and system interdependencies
in general nearly always rise dramatically. In reality, static and dynamic
properties are two \emph{different} things that have to be kept in different
places! Both can have a similar, hierarchical structure but each is a concept on
its own.

\emph{Interface} inheritance is used to implement \emph{Concerns} in a system.
\emph{Aspect Oriented Programming} (AOP) calls its concerns \emph{Aspects} and
uses special language means to implement them. With standard class constellations,
\emph{Design Patterns} provide clear solutions describing how best to combine
(associate/ inherit) classes. As subsumption of many design patterns, a
\emph{Framework} aims to provide basic functionality for the applications to be
embedded into it. All these efforts are based upon OOP. The main idea behind them
is to prevent code duplication and to minimize the interdependencies between
parts of a system. But what if OOP is one reason for just those interdependencies?

Big systems with a multitude of associations and dependencies often lead to a
loss in overview which results in so called \emph{Spaghetti Code}.
\emph{Component Oriented Programming} (COP) tries to solve this by encapsulating
code in smaller \emph{Components} which shall make it easier to keep overview.
People started to dream about a simple combination of such components and called
it the \emph{LEGO Metapher} (with relation to the building blocks for children).
But software models are not simple building blocks that could be built
\emph{Stone-on-Stone}! They are concepts as known from \emph{Human Thinking}.

The components described to here are \emph{passive} because they need a system
to call them. More recent studies are about \emph{active} components, sometimes
called \emph{Agents}. These are self-acting processes that solve special tasks.
The concepts behind are called \emph{Agent Oriented Programming}.

Passive components and all of the programming concepts described before them
belong to the \emph{Logical Architecture} of a system. The term
\emph{Physical Architecture} is used when it comes to active components, agents,
processes or systems in general.
