%
% $RCSfile: acknowledgements.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:05 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\section*{Acknowledgements}
\label{acknowledgements_heading}
%\addcontentsline{toc}{section}{Acknowledgements}

Certainly, first thanks is due my wife \emph{Kasia} and my \emph{Parents} and
\emph{Sisters}, being always with me, in good as in bad times. Not less
important to me are my aunt \emph{Maria Kosiza}, my great \emph{Relatives} and
our former chaplain \emph{Johannes Preis}, who have helped shaping me the way I
am.

I would like to thank my professor, \emph{Ilka Philippow}, for greatly
encouraging me during my work while leaving enough room to develop my own
ideas. Equal thanks is due my supervisors \emph{Dietrich Reschke} and
\emph{Mark Lycett}. \emph{Detlef Streitferdt} and \emph{Bernd D\"ane} gave
numerous hints improving the quality of the first part of my work. Consultation
with Bernd and \emph{Wolfgang Fengler} helped me understand Petri Net diagrams
and their hardware background as well as Assembler programming. Whenever I
got doubts about what I was doing, I was very lucky to receive good motivation
from my colleagues \emph{Volker Langenhan}, \emph{Oswald Kowalski},
\emph{Todor Vangelov} and \emph{Kai B\"ollert}. Oswald's talks about hardware
concepts made me find useful parallels to software. Alexander Fleischer helped
out when I was struggling with \LaTeX's paper size option.

My thanks go to my students \emph{Jens Bohl}, \emph{Torsten Kunze},
\emph{Dirk Behrendt}, \emph{Kumanan Kanagasabapathy}, \emph{Jens Kleinschmidt},
\emph{Martin Fache}, \emph{Karsten Tellhelm}, \emph{Marcel Kiesling},
\emph{Teodora Kikova}, \emph{Dennis Reichenbach}, \emph{Stefan Zeisler},
\emph{Michael Simon}, \emph{Henrik Brandes} and \emph{Saddia Malik} for
contributing their theses, tutorials or source code to the project. Special
thanks to \emph{Rolf Holzm\"uller} who brought in some innovative ideas for
CYBOL, in the final phase of my work, and helped cleaning many bugs in CYBOI.

Reminiscences on good times go to my former colleagues of \emph{OWiS Software}
who, together with the \emph{Technical University of Ilmenau} (TUI), have
contributed with great commitment to the development of the
\emph{Object Technology Workbench} (OTW) UML tool which I would have liked to
use in the early stages of my work. Pity it hasn't gone Open Source after its
development was stopped in 2000 :-( Thanks to \emph{Martin Wolf},
\emph{Rene Prei\ss{}el}, \emph{Dirk Henning} and all colleagues who have been
patient and well-explaining teachers!

I would like to acknowledge the contributors of \emph{CYBOP} \cite{cybop} and
\emph{Res Medicinae} \cite{resmedicinae}, especially all medical doctors, e.g.
\emph{Claudia Neumann} and \emph{Karsten Hilbert}, who supported the second
project with their analysis work \cite{resmedicinae2001} and mailing list
discussions. Furthermore, I want to mention \emph{Thomas Beale} from the
\emph{OpenEHR} project \cite{openehr} whose freely published design document
(back in 2001) gave me some initial ideas in the early stage of my work.
Acknowledged be all these brave \emph{Enthusiasts} of the
\emph{Free/ Libre Open Source Software} (FLOSS) community, who have provided me
with a great amount of knowledge through a comprising code base to build on.
I shall mention the contributors of FLOSS projects such as \emph{Scope}
\cite{scope}, \emph{Apache Jakarta} \cite{jakarta}, \emph{JOS} \cite{jos},
\emph{JDistro} \cite{jdistro}, the \emph{OpenHealth} \cite{openhealth} mailing
list readers, the \emph{OSHCA} \cite{oshca} members and all other supporters of
our projects and ideals.

Great thanks goes to the \emph{Urban und Fischer} publishing company, for
providing anatomical images from their \emph{Sobotta: Atlas der Anatomie}
\cite{urban} and to the \emph{Open Clip Art} project \cite{openclipart} for its
wonderful library of free art! Similarly, I have to thank the free online
dictionaries of \emph{LEO} \cite{leo} and the
\emph{Technical University of Chemnitz} \cite{tuchemnitz}.

I am grateful to all people who openly publish their knowledge on the web.
Without the numerous free sources, I would have never been able to accomplish
this work. Especially in the state-of-the-art part, I had to heavily rely on
existing sources. It is also therefore that I have decided to put my work under
the \emph{GNU FDL} licence \cite{gnulicences}. I would be happy to see large
parts of it copied in \emph{Wikipedia} \cite{wikipedia}!
