%
% $RCSfile: corrected_c.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:06 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\subsection{Corrected C}
\label{corrected_c_heading}
\index{C Programming Language Correction}
\index{Array with Meta Information}
\index{Termination Character-less Arrays}

Moreover, there is at least one incorrect implementation solution used in the C
standard libraries (\emph{libc}) and various traditional systems. Arrays are
all too often forwarded without necessary meta information like their
\emph{size} and \emph{count} of elements. But a pointer without additional
information about the size of the memory area (array) it points to is really
worthless. The introduction of \emph{Types} with defined size makes array
\emph{elements} countable, but does not solve the array size problem. A special
workaround, to what concerns \emph{string} arrays at least, was therefore
thought out. It requires that a null character ('$\backslash$0') be added as
termination to every character array which is to be interpreted as string.

But this is not a clean solution. For large systems, it pollutes a computer's
memory with thousands and thousands of termination suffixes, to compensate for
the missing size information. Recalling a recommendation on knowledge modelling
given in chapter \ref{knowledge_schema_heading}, meta information is that
\emph{about} other information (like an array) and should thus \emph{not} be
stored inside, but \emph{outside} the same (array). A further implementation
guideline made out and considered in CYBOI, is therefore:

\begin{itemize}
    \item[-] Use (character) arrays only together with their \emph{size} and
        \emph{count} of elements, not as \emph{null-terminated} strings! (Array
        references accompanied by necessary meta information make termination
        characters superfluous.)
\end{itemize}
