%
% $RCSfile: knowledge_split.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:07 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\subsection{Knowledge Split}
\label{knowledge_split_heading}

refer back to section \ref{input_output_and_rules_heading}

The \emph{Knowledge Query and Manipulation Language} (KQML) (section
\ref{knowledge_query_and_manipulation_language_heading}), a popular means of
communication in \emph{Agent Oriented Programming} (section
\ref{agent_oriented_programming_heading}), relies on \emph{Speech Act Theory}
developed by Searle 1960 and enhanced by Winograd and Flores in the 70s.
\cite{wikipedia} http://en.wikipedia.org/wiki/Agent\_communication\_language

- describe some language differences: CYBOL in comparison to Agent0:
http://www.cs.caltech.edu/~bond/courses/cs101c/agents16/node13.html
(states=believes, logic=capabilities, signal=commitment)
Do Agent0 and others provide the most suitable format to represent knowledge?

Two Comparison Tables:

1 with Agent0

http://www.cs.caltech.edu/~bond/courses/cs101c/agents16/node3.html

Mental State
    Beliefs (= Facts)
        ?? State Knowledge
    Commitments (to act, are grounded, that is do not contain variables)
        pre-defined actions are: DO, INFORM, REQUEST, UNREQUEST, REFRAIN, IF
        ?? Signal (signal removal is called "Release of a Commitment")
    Capabilities (= Actions; Commitments to oneself are special capabilities called Decision or Choice)
        ?? Logic Knowledge

Goals?
Intentions?
Time is treated as realtime; it is expressed explicitly, that is by adding it
to statements.
Action is represented by the fact that it happened at a given time;
since actions are facts they are also instantaneous.
Messages are passed by agents to each other, by message name.

2 with Kuehnel

- can all the different vocabulary (see Kuehnel: action, plan, assumption, aim/goal)
be simplified/unified into an easier system?
- Agents know about the environment and their own expertise
- add table for comparison between CYBOP and AGOP, for example:
    state knowledge = beliefs: capabilities (knowledge about itself)
        + constraints (knowledge about environment)
    logic knowledge = actions + plans
    signal = goal (aim)
- this is a comparison \emph{Trial} -- terms of AGOP are anyway not used uniformly in science

- ideas to split knowledge itself into state- and logic (action/ plan) knowledge
- see \cite[p. 95 ff., p. 125 ff.]{kuehnel}
