%
% $RCSfile: knowledge_engineering.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:07 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\section{Knowledge Engineering}
\label{knowledge_engineering_heading}
\index{Knowledge Engineering}
\index{KE}
\index{Data (Definition)}
\index{Information (Definition)}
\index{Knowledge (Definition)}
\index{Explicit Knowledge}
\index{Implicit Knowledge}
\index{Knowledge Representation}
\index{Date and Rule}

In order to correctly perform information input, memorising, processing and
output, systems need to know about the structure of the data they are
processing. While pure \emph{Data} abstract the real world in form of (mostly
machine-readable) characters (quality) and numbers (quantity) (more on this in
chapter \ref{knowledge_schema_heading}), their interpretation in a semantic
context may yield \emph{Information}. What coincides across the many different
definitions \cite{wikipedia} of the term \emph{Information}, are two
statements: it has to be recognisable and: it has to contain something new.
Organised information available in form of specific structures with
inter-relations is often called \emph{Knowledge}.

Quite often, knowledge gets shared into two kinds: \emph{explicit} (codified)
and \emph{implicit} (tacit). While the former, after \cite{nonaka}, referred to
knowledge that is transmittable in formal, systematic language, the latter had
a personal quality, which made it hard to formalise and communicate. This work
is about explicit knowledge; it wants to provide concepts and schemata for
expressing it as completely as possible (part \ref{contribution_heading}).

Over the years, many different \emph{Knowledge Representation} models have been
proposed. In software engineering, they represent different kinds of user
interfaces (textual, graphical, web), workflows, persistent- or transient data.
The biggest importance, however, models experience when representing a complete
\emph{Domain} (section \ref{domain_model_heading}), that is the special
business field an application system was developed for. After John F. Sowa
\cite{sowa}, \emph{Knowledge Engineering} (KE) could be defined as: \textit{the
branch of engineering that analyses knowledge about some subject and transforms
it to a computable form for some purpose.}

It has to be mentioned that the borders between \emph{Domain Engineering} (DE)
(section \ref{domain_engineering_heading}) and \emph{Knowledge Engineering} are
quite blurry. The \emph{Feature Model} (section \ref{feature_model_heading}),
although described as part of DE, can of course also be seen as one form of
knowledge representation, just like many other models. Both, DE as well as KE
specify formal languages and investigate how different models can be translated
into each other. This work, however, makes a split between DE and KE, because:

\begin{itemize}
    \item[-] their topics are usually treated as different fields of science
    \item[-] KE's focus is almost exclusively on representing (domain)
        knowledge in models
    \item[-] DE also considers their relation to the applications working on
        them
    \item[-] DE distinguishes models belonging to different phases in a
        \emph{Software Engineering Process} (SEP)
    \item[-] DE describes concrete implementation techniques
\end{itemize}

The following sections try to give a brief overview of the rather wide field of
knowledge representation and -engineering, raising only a few topics. Their
main intention is to show the existence of two different kinds of knowledge:
\emph{Date and Rule}, both of which can be structured according to an ontology,
what will be dealt with in the later chapters \ref{knowledge_schema_heading}
and \ref{state_and_logic_heading}.

%\input{undeterministic_knowledge}
\input{representation_principles}
\input{date_and_rule}
%\input{data_model}
%\input{knowledge_map}
\input{agent_communication_language}
\input{semantic_web}
%\input{temporary_section_summary}
