%
% $RCSfile: physical_architecture.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:08 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\chapter{Physical Architecture}
\label{physical_architecture_heading}
\index{Physical Architecture}
\index{Communication}
\index{Autonomous Systems}
\index{Interaction and Cooperation}
\index{Technical Systems}
\index{Computer}
\index{Client}
\index{Server}
\index{Communication Partners}
\index{System Constellations}
\index{Communication Languages}
\index{Information Technology Environment}
\index{IT}

\begin{flushright}
    \textsl{Simplicity is the Result of Maturity.}\\
    \textsc{Johann Christoph Friedrich von Schiller}
\end{flushright}

Software provides the functionality through which robots act and computers
represent and process information. Both are special kinds of machines which only
get useful for humans if they can be controlled and communicated with.
\emph{Communication} is an essential ability for almost any kind of system.
\emph{Autonomous} systems exist and may well be useful, but is it nearly always
the \emph{Interaction} and \emph{Cooperation} that makes technical systems (from
now on called \emph{Computer} in this work) so interesting and helpful to humans.

In many cases, systems are limited to one role: \emph{Client} or \emph{Server}.
Clients ask questions which servers answer. But both are able to send as well
as to receive information. One-way communication without any feedback is rarely
useful. Besides the mentioned client- and server-, there are other roles that a
computer system can take on when talking with so-called
\emph{Communication Partners}.

The following sections will stepwise build up- and briefly investigate some
examples of well-known system constellations and possible communication
languages that are commonly used in a general \emph{Information Technology}
(IT) environment. Because physical systems and their interactions are
considered without any knowledge about their inside, one also talks of this as
the \emph{Physical Architecture} of an IT environment. Its understanding is
important for later reflections on the inner architecture of software systems
(chapter \ref{logical_architecture_heading}). Also will chapter
\ref{state_and_logic_heading} come back to system communication principles and
introduce a translator architecture for universal communication.

\input{process}
\input{application_server}
\input{database_server}
\input{presentation_client}
\input{web_client_and_server}
\input{local_process}
\input{human_user}
\input{peer_node}
\input{remote_server}
\input{legacy_host}
\input{systems_interconnection}
\input{scalability}
\input{misleading_tiers}
