%
% $RCSfile: software_patents.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:08 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\section*{Software Patents}
\label{software_patents_heading}
%\addcontentsline{toc}{section}{Software Patents}

This work is about software. Software abstracts the real world, its items and
processes, and it can store these information and their relations which make up
actual \emph{Knowledge}. In the modern, so-called \emph{Information Society},
it becomes more and more important to have \emph{free} access to external
knowledge. This is an \emph{essential} human right and will decide about the
future living quality of people.

So much the important it is to \emph{prohibit} the application of patents to
software! They make an exclusive club of large companies own the rights on
banal, ordinary, day-to-day algorithms and methods that many people use. And,
they thereby kill any new ideas and hinder research efforts that depend on
these basic algorithms. If \emph{Software Patents} and patents on
\emph{Computer Implemented Inventions} (CII) got introduced, any free software
developer and especially \emph{Small- and Medium Sized Enterprises} (SME), the
driving force of innovation, could not unfold their full potential anymore,
since much of their time and effort would then have to go into patent inquiries
and costly legal disputes.

Software patents are dangerous for the free development of thoughts! Certain
lobbies exert an increasing influence on politics and push members of
parliaments to agitate and vote in their interest. Since probably every reader
of this document has an interest in informatics, every reader is also affected
by the software patent enforcement. But everybody can do something about it,
not only in Europe! Express your protest and sign the petition at \cite{ffii}!
