%
% $RCSfile: tags.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:09 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\subsubsection{Tags}
\label{tags_heading}
\index{CYBOL Tags}
\index{CYBOL 'model' Tag}
\index{CYBOL 'part' Tag}
\index{CYBOL 'property' Tag}
\index{CYBOL 'constraint' Tag}

There are many kinds of meta information besides the above-mentioned
attributes, that may be known about a model. These are given in special XML
tags called \emph{property} and \emph{constraint}. As defined in section
\ref{vocabulary_heading}, a CYBOL knowledge template may use four kinds of XML
tags:

\begin{itemize}
    \item[-] model
    \item[-] part
    \item[-] property
    \item[-] constraint
\end{itemize}

The \emph{model} tag appears just once. It is the root node which makes a CYBOL
knowledge template a valid XML document.

Of actual interest are the \emph{part} tags. They identify the models that the
\emph{whole} model described by the CYBOL knowledge template consists of.

A \emph{whole} model may know a lot more about its \emph{part} models, than is
given by a part model's XML attributes. A spatial state model may know about
the \emph{position} and \emph{size} of its parts, in space. A temporal model
(such as a workflow) may have to know about the \emph{position} of its parts in
time, in order to be able to execute them in the correct order. Further, the
temporal model needs to know about the \emph{input/output} (i/o) state models
which are to be manipulated by the corresponding logic operation (part model).
The number of parts within a whole (compound) model may be limited. And so on.
These additional information are provided by \emph{property} tags whose number
is conceptually unlimited.

Not only parts need additional meta information; properties may need such
information, too. The position or size as properties of a part may have to be
constrained to certain values, such as a \emph{minimum} or \emph{maximum}. The
values of the \emph{colour} property of a part model may have to be chosen out
of a pre-defined set called \emph{choice}. Information of that kind are stated
in \emph{constraint} tags.

Since the number of possible meta information implementable in CYBOL is already
quite large and steadily growing, as the development continues, this section
cannot list them all. At a future point in time, a more-or-less complete CYBOL
specification document may be found at the CYBOP project's website \cite{cybop}.
