%
% $RCSfile: teleportation.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:09 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\paragraph{Teleportation}
\label{teleportation_heading}
\index{Teleportation}
\index{Beaming}
\index{DNA}
\index{Body}
\index{Brain}
\index{Mind}
\index{Abstraction}
\index{Key-Value Pair}

One dream of research is \emph{Beaming} (\emph{Teleportation}),
that is the transfer of matter in space.
It seems very unlikely that big pieces of matter and their structures can be
transferred. Looking at current transfer mode systems, it is not matter but
abstractions of it which get transferred. Radio transfers acoustical signals;
Television additional visual signals and so on. The visual signals consist of
sequences of images which are abstract illustrations of some place or scene.
These abstractions are transported in form of electromagnetic waves and later
displayed on a screen by either electrons (cathod ray tube) or thin film
transistors. Once again: not matter gets transferred but information.

Assuming that beaming really worked one day, it seems to become the easier part
to build a new body after the model encrypted in a transmitted human \emph{DNA}.
(This would be the same as \emph{Cloning} and in the same way, body damages
could be repaired, too, which could lead to neverending life.)

A physical \emph{Brain} might get copied or transferred, but how much more difficult
would this be with the \emph{Knowledge} contained in it? When building a body copy,
billions of \emph{Neurons} and their weighted \emph{Connections} have to be
duplicated identically. It is still not clear if the \emph{Mind}/ \emph{Character}/
\emph{Personality} would then really be preserved.

For both problems (transfer of \emph{Brain} and \emph{Mind}), \emph{Abstractions}
are essential. They are a precondition for beaming to function correctly. The DNA
represents the model of the body, abstracted to a chain of \emph{Key-Value Pairs}.
The Neurons and their connections as \emph{Network of Weights} stand for the mind.
If body and mind can be abstracted in complete, with no information-loss,
\emph{direct} knowledge exchange between human brains becomes possible. Also,
body and mind can be stored in form of models, for a longer period of time.
