%
% $RCSfile: tool_support.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:09 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\section{Tool Support}
\label{tool_support_heading}
\index{CYBOL Tool Support}

When proposing a new theory of computing, or a new programming language, it is
common to provide a suitable \emph{Integrated Development Environment} (IDE)
supporting the application of that theory or language. If not the tools
themselves, a recommendation for how they may look like should be given at
least. This is what the following sections try to achieve.

\input{template_editor}
\input{knowledge_designer}
\input{model_viewer}

To what concerns the usage of existing UML tools for modelling CYBOL
applications, it has to be said that they are most likely not able to support
CYBOP models, nor can they be easily adapted. Even though the diagram
specifications may be similar, the underlying programming principles and model
repositories are just too different. It might be possible, however, to create
interfaces partly translating CYBOL-encoded (XML) models into UML models,
possibly using the \emph{XML Metadata Interchange} (XMI) standard or the like.
It will presumably be easier to translate CYBOL- into UML models, than vice
versa, because CYBOL is very expressive. While CYBOL knowledge templates
distinguish between whole-part- and meta elements, for example, UML models do
not. Another point is that CYBOL holds state- and logic knowledge in separate
templates, that would have to be merged into common classes when being
translated into UML. But the investigation and evaluation of further details
concerning the tool support is left for future works.
