%
% $RCSfile: typeless_programming.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:09 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\subsection{Typeless Programming}
\label{typeless_programming_heading}
\index{Typeless Programming}
\index{Scripting Language}
\index{Job Control Language}
\index{Batch Language}
\index{Perl}
\index{Python}
\index{Rexx}
\index{Tcl}
\index{Visual Basic}
\index{VB}
\index{Universal Interactive Executive}
\index{UNIX}
\index{Script Oriented Programming}
\index{SOP}
\index{Dynamic Typing}
\index{System Integration Language}
\index{Glue Language}

\emph{Scripting Languages} (formerly also called \emph{Job Control-} or
\emph{Batch Languages} \cite{wikipedia}) such as Perl \cite{wall}, Python
\cite{lutz}, Rexx \cite{ohara}, Tcl \cite{ousterhout1994}, \emph{Visual Basic}
(VB) and the \emph{Universal Interactive Executive} (UNIX) shells overcome the
disadvantages of system programming languages (section
\ref{system_programming_heading}) by being \emph{typeless} and
\emph{interpreted}. The paradigm behind them is sometimes called
\emph{Script Oriented Programming} (SOP).

Ousterhout \cite{ousterhout1998} writes that modern computers were fundamentally
typeless: any word in memory could hold any kind of value, such as an integer, a
floating-point number, a pointer, or an instruction. The meaning of a value were
determined by how it is used: if the program counter pointed at a word of memory
then it were treated as an instruction; if a word were referenced by an integer
\emph{add} instruction then it were treated as an integer; and so on. The same
word could be used in different ways at different times (what is also called
\emph{Dynamic Typing}).

Because scripting languages are intended primarily for plugging together existing
components, they are also referred to as \emph{System Integration Languages} or
\emph{Glue Languages}. They provide a higher level of programming than assembly-
or system programming languages. Through their usage, integrated applications,
after \cite{ousterhout1998}, could be developed five to ten times faster than
with system programming languages. Scripting languages sacrifice execution speed
to improve development speed.

The interpreter described in chapter \ref{cybernetics_oriented_interpreter_heading}
is able to handle data (knowledge) without knowing about their type (kind of
abstraction) in advance, that is at compilation time. Although itself written
in the system programming language \emph{C}, the interpreter is very flexible
when it comes to processing knowledge.
