%
% $RCSfile: collection.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:05 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\paragraph{Collection}
\label{collection_heading}
\index{Collection}
\index{Array}
\index{Allocated Area}
\index{Random Access Memory}
\index{RAM}
\index{Vector}
\index{Stack}
\index{Last-In-First-Out}
\index{LIFO}
\index{Set}
\index{List}
\index{Duplicate Element}
\index{Ordered Collection}
\index{Sequence}
\index{Enumeration}
\index{nextElement Method}
\index{Java Development Kit}
\index{JDK}
\index{Iterator}

The \emph{Array} is the most basic form of a container. It represents an allocated
area in the computer's \emph{Random Access Memory} (RAM). A \emph{Vector}
implements a dynamically growable array of objects. The \emph{Stack} class extends
the vector class and represents a \emph{Last-In-First-Out} (LIFO) stack of objects.
A collection that contains no duplicate elements is called a \emph{Set}. Unlike
sets, \emph{Lists} typically allow duplicate elements. Synonyms for list are
\emph{Ordered Collection} and \emph{Sequence}.

Objects that can generate a series of elements, one at a time, implement the
\emph{Enumeration} interface. Successive calls to the \emph{nextElement} method
return successive elements of such a series. In recent releases of the
\emph{Java Development Kit} (JDK) \cite{java}, \emph{Iterator} takes the place
of enumeration, in the collections framework. An iterator over a collection
differs from an enumeration in that it allows the caller to remove elements,
with well-defined semantics, from the underlying collection during an iteration.
