%
% $RCSfile: component_oriented_programming.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:06 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\section{Component Oriented Programming}
\label{component_oriented_programming_heading}
\index{Component Oriented Programming}
\index{COP}
\index{Component Based Design}
\index{CBD}
\index{Software Component}
\index{Component}
\index{Black Box Reuse}
\index{Graphical User Interface}
\index{GUI}
\index{Delphi}
\index{Visual Component Library}
\index{VCL}
\index{Visual Basic}
\index{VB}
\index{Java}
\index{Abstract Window Toolkit}
\index{AWT}
\index{Bean}
\index{Agent}
\index{Open Source Software}
\index{OSS}
\index{Legacy System}
\index{PL/1}
\index{Interface Definition Language}
\index{IDL}
\index{Common Object Request Broker Architecture}
\index{CORBA}
\index{Aspect Oriented Programming}
\index{AOP}
\index{Aspect}
\index{Concern}
\index{Agent Oriented Programming}
\index{AGOP}
\index{Agent}

In the not-so-distant past, there has been a lot of buzz in the industry
touting \emph{Component Based Design} (CBD). Much of it was more marketing than
the actual application of new design principles and it is also no surprise that
the definition of a \emph{Software Component} differs between authors, companies
and projects. A rather formal one is that of the \emph{Avalon} framework
\cite{avalon} of the \emph{Apache Jakarta} project \cite{jakarta}, which says:

\begin{quote}
    \emph{Component Oriented Programming} takes object-oriented programming one
    step further. Regular object-oriented programming organizes data objects
    into entities that take care of themselves. There are many advantages to
    this approach. \ldots\ But it also has a big limitation: that of object
    \emph{Co-Dependency}. To remove that limitation, a more rigid idea had to
    be formalized: the \emph{Component}. The key difference between a regular
    object and a component is that a component is completely replaceable
    (\emph{Black Box Reuse}).
\end{quote}

Many kinds of software components exist: There are \emph{Graphical User Interface}
(GUI) components known from Delphi's \emph{Visual Component Library} (VCL)
\cite{delphi}, from \emph{Visual Basic} (VB) \cite{visualbasic} or Java's
\emph{Abstract Window Toolkit} (AWT) \cite{java}, which calls its components
\emph{Beans}; there are \emph{Business} components containing domain knowledge
and \emph{Technical} components interacting with infrastructure systems like
\emph{CORBA-}/ \emph{EJB-}/ \emph{DCOM} middleware, with a \emph{Database} (DB)
or \emph{Operating System} (OS) (sections \ref{database_server_heading},
\ref{remote_server_heading}); there are general \emph{Application} components
as investigated by \emph{Avalon} \cite{avalon}. Whole systems, that is
self-acting components, are often called \emph{Agents} (section
\ref{agent_oriented_programming_heading}).

The following sections deal with application components whose principles are
investigated on the example of the \emph{Avalon} framework, because that is an
\emph{Open Source Software} (OSS) project providing all sources for free. After
\emph{Avalon} \cite{avalon}, \emph{Component Oriented Programming} (COP) were
not necessarily the same as \emph{Component Based Design} (CBD). The latter
referred to how a system is \emph{designed}; the former to how it is
\emph{implemented}. In practice, one could not implement COP without first
designing with components in mind.

By following CBD rules, software projects try to integrate most diverse systems
into one environment. Although the systems should ideally use COP for the
implementation of their components, this is not a must. Legacy systems (section
\ref{legacy_host_heading}) can be encapsulated as well \cite{brown2000}, acting
as one component to the outside environment. A \emph{Service} offered by a legacy
system written in \emph{PL/1} \cite{pli}, for example, may be designed and
treated as component. It may be accessed via \emph{Interface Definition Language}
(IDL) interfaces and use a \emph{Common Object Request Broker Architecture}
(CORBA) for communication. The interna of such a system, however, do neither
have to follow component- nor object-oriented programming principles.

The following sections describe popular COP techniques. Although being
researched in an own scientific field, \emph{Aspect Oriented Programming} (AOP)
principles are added as sub-section, because \emph{Aspects} are comparable to
the \emph{Concerns} of COP. For similar reasons, \emph{Agent Oriented Programming}
(AGOP) techniques are described following, because \emph{Agents} can be seen as
self-acting \emph{Components}. All of them, that is COP's concerns, AOP's
aspects and AGOP's agents owning a knowledge base will be recalled once again
in part \ref{contribution_heading} of this work.

\input{inversion_of_control}
\input{component_lifecycle}
\input{interface_and_implementation}
\input{separation_of_concerns}
\input{spread_functionality}
\input{aspect_oriented_programming}
\input{agent_oriented_programming}
