%
% $RCSfile: replication.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:08 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\subsection{Replication}
\label{replication_heading}

When humans sense something that is strange to them, their mind \emph{compares}
that thing to already known models (concepts) and such tries to understand the
new item. One might say the human mind uses existing knowledge to gain new
knowledge.

If the new model is similar to a known concept, it can be understood as
\emph{Clone} of that concept, that is their gross structure is identical and
variations are only in details.
If the new concept differs from the concept it is compared with, a
\emph{Translator} becomes necessary to exchange knowledge between the two.

Comparand

\emph{Comparison} is an everyday action of the human mind. It becomes possible
through \emph{Categorisation} (section \ref{category_heading}).

If two \emph{Comparands}, for example a \emph{Residential Building} and a
\emph{Factory Building}, are to be compared, the human mind creates a common
\emph{Super Category} \emph{Building} that sums up their common properties.
Both will be recognised as \emph{Building} because they consist of \emph{Walls},
a \emph{Roof}, \emph{Windows} and a \emph{Door} -- a concept that is known to
the mind. These common properties serve as comparison \emph{Criteria}.

It is the properties that can be compared.
But state/logic models need to belong to the \emph{same} type of model.
--> need to be defined/constrained!
logic:
- create/destroy operation
- copy/move operation
- receive/send operation
- boolean/arithmetic operation
state:
- gui
- tui
- wui
- all file/data formats that are useful in a special context

Clone

The human mind can make things \emph{seem} identical (by neglecting differing
properties), yet in reality nothing in existence really is. A \emph{Clone} of a
\emph{Human Being} may be created from the same genetical information, but the
atoms it consists of are different from those of the original. A \emph{Paper}
with a technical drawing may get copied but it is physically not identical to
its original.

What can be identical, however, is abstract \emph{Knowledge}. The concept of the
\emph{Technical Drawing} remains the same, on the original and on the copied paper.
The \emph{Genetical Information} of a human being and its clone are identical.
The human mind stores and works with abstract knowledge. It can therefore create
identical models and use them for thinking and understanding.

But identical models per se are not very helpful. A known concept represents
known knowledge and it does not make sense to duplicate that. \emph{Cloning} only
becomes useful when using an original as \emph{Template} for a new model with
altered properties.

Basically, every model can become a template (often called \emph{Type}), by being
cloned. The resulting clone is sometimes called \emph{Instance}. It has an own
identity and is not a clone any longer as soon as it obtains its own character by
changing existing or adding new properties. In fact, cloning (\emph{Instantiation})
is the same as creating a sub category to an existing category (\emph{Subtyping}).
Saying it the other way: \emph{Typification} is the same as \emph{Categorisation}.

Three examples shall be given to demonstrate that:
The concrete person \emph{Aristotle} can be seen as instance of type
\emph{Human Being}. Cloning that person genetically, it becomes a type (category)
itself. All person clones and their original belong to the same category of people
with identical genetical information.
The books in a library are instances of the common type \emph{Book}.
...
- UNIX processes are cloned

- Child is physically created (born) by mother with one DNA
- beforehand, father contributed his genes (DNA) which got mixed with the mother's
- multiple inheritance; interference of two different concepts??
