%
% $RCSfile: semantic_web.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:08 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\subsection{Semantic Web}
\label{semantic_web_heading}
\index{Semantic Web}
\index{Extensible Markup Language}
\index{XML}
\index{XML Schema}
\index{XML Data}
\index{Document Content Description}
\index{DCD}
\index{Schema for Object Oriented XML}
\index{SOX}
\index{XML Metadata Interchange}
\index{XMI}
\index{Resource Description Framework}
\index{RDF}
\index{Web Ontology Language}
\index{OWL}

As mentioned in section \ref{extensible_markup_language_heading}, the
\emph{Extensible Markup Language} (XML) \cite{rdfowlrelease} provides a:
\textit{set of rules for creating vocabularies that can bring structure to both
documents and data on the Web} and it: \textit{gives clear rules for syntax.}
XML Schemas \cite{xmlschema} served as: \textit{a method for composing XML
vocabularies.} Yet although XML were a powerful, flexible surface syntax for
structured documents, it imposed no \emph{Semantic Constraints} on the
\emph{Meaning} of these documents. Having investigated the usefulness of XML
for a \emph{meaningful} sharing of information units at the semantic level,
Robin Cover writes \cite{xmlsemantics}:

\begin{quote}
    \ldots\ the use of XML for \emph{Data Interchange} may already outweigh its
    use for \emph{Document Display}. For messaging and other transaction data,
    specifications approaching the level of formal semantics (e.g. KIF or KQML)
    are desirable, governing not just common (atomic) data types in business
    objects, but complex objects used by computer agents in large-scale business
    transactions. XML vocabularies supporting these applications will need to be
    defined in terms of precise object semantics.
\end{quote}

He lists a number of efforts dealing with the support for generic XML semantics,
that is \emph{Semantic Transparency} of XML in a broader sense, to provide
unambiguous semantic specification:

\begin{itemize}
    \item[-] \emph{XML Data} \cite{xmldata}
    \item[-] \emph{Document Content Description} (DCD) for XML \cite{dcd}
    \item[-] \emph{Schema for Object Oriented XML} (SOX) \cite{sox}
    \item[-] \emph{XML Metadata Interchange} (XMI) \cite{mda}
    \item[-] \emph{Resource Description Framework} (RDF) \cite{rdf}
    \item[-] \emph{Web Ontology Language} (OWL) \cite{owl}
\end{itemize}

The RDF and OWL as well-known efforts are mentioned in the following two
subsections. Both are often comprised under the umbrella term
\emph{Semantic Web}. Much of what is written about the semantic web sounds as
if it was a replacement technology for the Web as known today. Yet Eric Miller,
leader of W3C's semantic web activity, means \cite{rdfowlrelease}:

\begin{quote}
    In reality, it's more Web Evolution than Revolution. The Semantic Web is
    made through incremental changes, by bringing machine-readable descriptions
    to the data and documents already on the Web. XML, RDF and OWL enable the
    Web to be a global infrastructure for sharing both, documents and data which
    make searching and reusing information easier and more reliable as well.
\end{quote}

\input{resource_description_framework}
\input{web_ontology_language}
