%
% $RCSfile: signal_checking.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:08 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\subsection{Signal Checking}
\label{signal_checking_heading}
\index{CYBOI Signal Checking}

The \emph{check} procedure consists of an endless loop continuously checking
for signals residing in signal memory. It provides the dynamics and -- so to
say -- keeps the system \emph{alive}. Of all queued signals, the one with
highest priority is retrieved first and forwarded to the \emph{handle}
procedure (\emph{handler} module).

This principle can be observed not only in operating-, but many other kinds of
systems. \emph{Servers} run an endless loop waiting for (network) \emph{Client}
requests. Applications often use signalling mechanisms provided by a framework,
that handles keyboard press- or mouse click signals stemming from a
\emph{Graphical User Interface} (GUI). However, as opposed to the event
handling of such frameworks which relies on bidirectional dependencies since
child components have to register as listener at their parent, a top-level
signal checker loop forwards all events in a unidirectional manner to
interested system parts. It is worth noting that signals may also be produced
internally, as follow-ups, by other signals.

After having been processed, the signal gets removed from the signal memory.
Once an \emph{exit} signal occurs, the shutdown flag is set, so that the signal
checking loop can be left -- and the system be shutdown.
