%
% $RCSfile: used_libraries.tex,v $
%
% Copyright (C) 2002-2008. Christian Heller.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1 or
% any later version published by the Free Software Foundation; with no
% Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% Version: $Revision: 1.1 $ $Date: 2008-08-19 20:41:09 $ $Author: christian $
% Authors: Christian Heller <christian.heller@tuxtax.de>
%

\subsection{Used Libraries}
\label{used_libraries_heading}
\index{CYBOI using External Libraries}

Before interpreting a stream of CYBOL data, a parser has to bring structure
into it. Since CYBOL bases on the XML standard, one option was to use one of
the many existing XML parser libraries \cite{dom, sax}, for reading and writing
CYBOL sources. The current CYBOI version uses \emph{libxml2}, the
\emph{GNU Network Object Model Environment} (GNOME) XML library, written in C.

Existing libraries, however, bring with a lot of functionality, not all of
which is actually used in CYBOI. A future version will therefore contain its
own parsing procedures, tailored to CYBOI's needs. Another argument therefor
are special requirements (differing XML attribute \emph{begin} and \emph{end}
characters) when serialising knowledge models into CYBOL files.

Further libraries are needed. The \emph{X Window System} (X) \emph{X Libraries}
(Xlibs), for example, contain routines to use \emph{Graphical User Interfaces}
(GUI) under UNIX-like \emph{Operating Systems} (OS); for a Windows OS, it would
be the \emph{Graphics Device Interface} (GDI). The \emph{UNIX Socket's} pendant
in the Windows world is the \emph{Windows Socket} (WINSOCK), both serving as
communication mechanism. A \emph{Textual User Interface} (TUI) for the UNIX
console is programmed differently than one for a \emph{Disk Operating System}
(DOS) shell. And so on. Because of the steady changes in CYBOI's source code,
and not to let this work's volume exceed the worst expectations, these shall
not be elaborated on here.
