%
% $RCSfile: summary.tex,v $
%
% Copyright (c) 2001-2004. Christian Heller. All rights reserved.
%
% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.1
% or any later version published by the Free Software Foundation;
% with no Invariant Sections, with no Front-Cover Texts and with no Back-Cover
% Texts. A copy of the license is included in the section entitled
% "GNU Free Documentation License".
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% @author Christian Heller <christian.heller@tuxtax.de>
% @author Jens Bohl <info@jens-bohl.de>
%

\section{Summary}
\label{summary_heading}

Software patterns are essential elements of frameworks. This paper showed how they
can be combined to comprise their advantages and to realize hierarchical structures
with unidirectional dependencies.\\
These structures can be created and properly destroyed using the lifecycle of
components. In that lifecycle, object relations become more transparent and are
easier to control and to maintain. As an extension, this paper introduced the
\emph{globalize} method by which references to globally needed objects can be
forwarded through a system which eliminates the need for static methods or objects.\\
Ontologies can help to model particular domains and to layer software. Every level
of these ontologies has a particular supertype, whereby these types depend on each
other by inheritance. This concept supports the modelling and logical separation
of software into hierarchical architectures. The granularity of the ontology
(number of ontological levels) can be adapted to particular needs.\\
In the course of this document, it turned out that hierarchies are not only ideal
for structuring domain knowledge but also for structuring whole systems (applications).
As essential design decision to take, this paper proposed to introduce a top-most
super class (called \emph{Item} here) which represents a \emph{Map} container.
Thousands of lines of code in form of \emph{set} and \emph{get} methods can such
be eliminated which leads to a tremendous code reduction and improved clarity.\\
By applying the new concepts introduced in this document, the quality of software
can hopefully be increased. The time for building systems might get reduced.
The clear architecture should avoid common confusion as the systems grow.

