%
% $RCSfile: reflection.tex,v $
%
% Copyright (c) 2001-2004. Christian Heller. All rights reserved.
%
% No copying, altering, distribution or any other actions concerning this
% document, except after explicit permission by the author!
% At some later point in time, this document is planned to be put under
% the GNU FDL license. For now, _everything_ is _restricted_ by the author.
%
% http://www.cybop.net
% - Cybernetics Oriented Programming -
%
% http://www.resmedicinae.org
% - Information in Medicine -
%
% @author Christian Heller <christian.heller@tuxtax.de>
%

\subsection{Reflection}
\label{reflection_heading}

The use of a programming language eases model abstraction for human programmers.
Special tools exist that break down models given in form of program code into
their binary form, into sequences of \emph{0} and \emph{1}. These are called
\emph{Machine Language}, because understood by computers.

Classical programming languages have the linguistical means to express high-level
\emph{Knowledge} as well as low-level \emph{Hardware Control Instructions}. The
use of such languages inevitably leads to a mess in program code because both are
mixed up. Unflexible, overly complex systems with numerous interdependencies are
the result. Section \ref{traditional_programming_heading} already criticised this
weakness of traditional programming language concepts. This work makes the
necessary split: Knowledge gets \emph{separated} from hardware control.

\subsubsection{Biological Cell Separation} is one proof for this theory.
The original cell forwards its configuration information in form of a
\emph{Desoxy Ribo Nucleic Acid} (DNA) to the new cell. The new cell uses this
knowlege to create new organelles and to function correctly. Each cell represents
a system with different \emph{Hardware} that it controls but all cells (in one-and-
the-same biological creature) use the same configuration.

\subsubsection{Regions of the Human Brain} are another example. The main knowledge
is stored in the \emph{Cerebral Cortex}. Other regions more or less just control
the exchange of knowledge through input/ output organs (hardware), for
communication with other biological systems.
